---
title: "Usage Examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{advanced-usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(r4googleads)
google_auth <- authenticate()
```

## Examples

In addition to Google queries {r4googleads} comes with built-in support 
for GoogleAds services and listing accessible customers. Please notice that all examples assume that you have a working GoogleAds setup (MCC, Client ID, Client Secret, Developer Token and client token) and that you're authenticated successfully using {r4googleads}.


### Explore Report Data Schema

First create the corresponding R object of class *GoogleAdsFields* and set its 
parameters that will be send to Google. 

```R
report_schema = googleAdsFields(
  tbl = "campaign", # e.g. campaign report
  api_version = 'v9'
  )

```

Pass the newly created object to the standard *query_google_ads* function

```r

campaign_report_schema <- query_google_ads(
  mcc_id = '***-***-****', # Google Ads My Client Center ID
  google_auth = google_auth,
  service = report_schema,
  raw_data = F
)
```

and received the desired answer based on the parameters and class of the object. 

```r
> str(campaign_report_schema)
List of 13
 $ resourceName      : chr "googleAdsFields/campaign"
 $ category          : chr "RESOURCE"
 $ dataType          : chr "MESSAGE"
 $ name              : chr "campaign"
 $ selectable        : logi FALSE
 $ filterable        : logi FALSE
 $ sortable          : logi FALSE
 $ selectableWith    : chr [1:194] "accessible_bidding_strategy" "bidding_strategy" "campaign_budget" "customer" ...
 $ attributeResources: chr [1:4] "accessible_bidding_strategy" "bidding_strategy" "campaign_budget" "customer"
 $ metrics           : chr [1:84] "metrics.absolute_top_impression_percentage" "metrics.active_view_cpm" "metrics.active_view_ctr" "metrics.active_view_impressions" ...
 $ segments          : chr [1:24] "segments.ad_destination_type" "segments.ad_network_type" "segments.click_type" "segments.conversion_action" ...
 $ typeUrl           : chr "com.google.ads.googleads.v9.resources.Campaign"
 $ isRepeated        : logi FALSE

```


### List Customers / Accounts

Listing available accounts works in similar fashion. 

```R
list_customer_service <- listAccessibleCustomers(api_version = 'v9')

customers <- query_google_ads(
  mcc_id = '***-***-****', # Google Ads My Client Center ID
  google_auth = google_auth,
  service = list_customer_service,
  raw_data = F
)
```

... customers a simple list of resources.


```r
> customers
$resourceNames
[1] "customers/8880XXXXX"

```





