---
title: "developer-guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{developer-guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(r4googleads)
```


Let's put some details about our S3 method dispatch here. Also add a contribution guide.

### Explore Report Data Schema

```R
report_schema = googleAdsFields(
  tbl = "campaign", # e.g. campaign report
  api_version = 'v9'
  )

campaign_report_schema <- query_google_ads(
  mcc_id = '***-***-****', # Google Ads My Client Center ID
  google_auth = google_auth,
  service = report_schema,
  raw_data = F
)
```

#### List Customers / Accounts

```R
list_customer_service <- listAccessibleCustomers(api_version = 'v9')

customers <- query_google_ads(
  mcc_id = '***-***-****', # Google Ads My Client Center ID
  google_auth = google_auth,
  service = list_customer_service,
  raw_data = F
)
```

## Contribution and Package Extension

{**r4googleads**} makes use of the [REST interface](https://developers.google.com/google-ads/api/rest/overview) of the Google Ads API. For each REST resource / service of the Google Ads API we construct a S3 Class in `R/google_services_construtors.R`. This modular approach enables the extension of {**r4googleads**} service by service.
