---
title: "RAdwords Migration Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{radwords-migration-guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(r4googleads)
```

## RAdwords Migration Guide - Migrating your R Code from the Adwords API towards the new Google Ads API with {**r4googleads**}

Over the last couple of years Google developed a new API for its Google Ads services. On 27th of April 2022, Google will shut down the old Adwords API. By the end of April any R code relying on our RAdwords package will be deprecated. In order to keep your code and data tasks up an running, you need to refactor your R code to be compatible with new Google Ads API. We created a new R package {**r4googleads**} that will replace our RAdwords package. {**r4googleads**} provides you the full functionality of RAdwords plus additional new features!

Start migrating your code now with our easy step-by-step guide!

## Installation

To install the latest stable version of {**r4googleads**} from R's official Comprehensive R Archive Network (CRAN) run

```r{eval=FALSE,message=FALSE, warning=FALSE}
install.packages("r4googleads")
```

or install the latest development release from GitHub using the [{remotes}](https://cran.r-project.org/web/packages/remotes/index.html) R package. 
(the below example code assumes the {remotes} package has been installed previously.)

```R
remotes::install_github("banboo-data/r4googleads")
```

## Authentication with the API

The authentication process of RAdwords and {**r4googleads**} remains the same (beside the function name). This means you can just start using the {**r4googleads**} package with your existing RAdwords authentication objects (tokens). The good news is you don´t have to run through the whole authentication process and you can just start working on the code migration!


The previous RAdwords authentication:

```R
google_auth <- doAuth()
```

The {**r4googleads**} authentication now is:

```R
google_auth <- authenticate()
```

## Loading Data

{**r4googleads**} enables you to apply the Google Ads Query Language directly. This means you can write your own SQL like syntax or use the [Query Builder](https://developers.google.com/google-ads/api/fields/v9/overview_query_builder) provided by Google.

The previous RAdwords code:

```R
body <- statement(select = c('CampaignName', 'Clicks', 'Cost'),
                  report = "CAMPAIGN_PERFORMANCE_REPORT",
                  start = "2022-01-01",
                  end = "2022-01-10")
                  
data <- getData(clientCustomerId = 'XXX-XXX-XXXX', #use Adwords Account Id (MCC Id will not work)
                google_auth = google_auth,
                statement = body)
```

Loading data with {**r4googleads**}:


```R
sql_query <- "SELECT campaign.name, metrics.clicks, metrics.cost_micros
              FROM campaign
              WHERE segments.date BETWEEN '2022-01-01' AND '2022-01-10'
              AND metrics.impressions > 0
              PARAMETERS include_drafts=true"

query_service <- googleAdsSearch(
  aid = 'XXX-XXX-XXXX', # Google Ads Accountr ID
  query = sql_query,
  api_version = 'v9'
)

data <- query_google_ads(
  mcc_id = 'XXX-XXX-XXX', # Google Ads My Client Center ID
  google_auth = google_auth,
  service = query_service,
  raw_data = F
)
```


## Exploring the API

With RAdwords you could explore the report types of the Adwords API with the `reports()` and `metrics()` methods.
In {**r4googleads**} you can explore the available [Google Ads API reports](https://developers.google.com/google-ads/api/fields/v9/overview) with:

```R
tbl_schema_service = googleAdsFields(tbl = "campaign", api_version = 'v9')

tbl_schema <- query_google_ads(
  mcc_id = 'XXX-XXX-XXXX',
  google_auth = tbl_schema_service,
  service = my_service_2,
  raw_data = F
)
```

## Overview of functions and methods

| Functionality     | RAdwords             | r4googleads        |
|:------------------|:--------------------:|-------------------:|
| Authentication    | doAuth()             | authenticate()     |
| Define Query      | statement()          | googleAdsSearch()  |
| Loading Data      | getData()            | query_google_ads() |
| Reports & Metrics | reports(); metrics() | googleAdsFields()  |
